---
title: "Web Mining"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
---
```{r}

library("rvest")
library("ggmap")
library("leaflet")
library("flexdashboard")
library("ggplot2")
library("plotrix")
library("gridExtra")
```
All Football Matches
===================================== 
***
About The Data

All data about matches taken from http://www.sportsevents365.com   

### All Matches

```{r}
League <- c("uefa-europa-league","la-liga","serie-a","premier-league","bundesliga","french-ligue-1","2018-world-cup","2017-confederations-cup")
Tickets <- data.frame()
for(x in League){
  url <- paste("http://www.sportsevents365.com/dock/competition/", 
             x, sep="")
  webpage <- read_html(url)
  Tickets_Names = webpage%>% html_nodes(css=".colorA span") %>% html_text()
  Tickets_Names <- gsub("\n","",Tickets_Names)
  Tickets_Names <- gsub("\t","",Tickets_Names)
  Tickets_Names <- gsub(" ","",Tickets_Names)
  Tickets_Names = as.data.frame(Tickets_Names)
  Location = webpage%>% html_nodes(css=".eventLocation div") %>% html_text()
  Location <- gsub("\n","",Location)
  Location <- gsub("\t","",Location)
  Location <- gsub(" ","",Location)
  Location_Coordinates <- geocode(Location)
  Location = as.data.frame(Location)
  Match_Time = webpage%>% html_nodes(css=".icon+ span") %>% html_text()
  Match_Time <- gsub(",","",Match_Time)
  Match_Time = as.data.frame(Match_Time)
  Tickets_Price = webpage%>% html_nodes(css=".stories .tableCell:nth-child(3)") %>% html_text()
  Tickets_Price <- gsub("from","",Tickets_Price)
  Tickets_Price <- gsub("€","",Tickets_Price)
  Tickets_Price <- gsub("\n","",Tickets_Price)
  Tickets_Price <- gsub("\t","",Tickets_Price)
  Tickets_Price <- as.numeric(Tickets_Price)
  Tickets_Price <- as.data.frame(Tickets_Price)
  All = cbind(Tickets_Names ,Location ,Location_Coordinates,
                              Match_Time ,Tickets_Price,League=x )
  All = as.data.frame(All)
  Tickets <- rbind(Tickets, All)
}
Tickets$Tickets_Price[is.na(Tickets$Tickets_Price)] <- 0
#t <- leaflet() %>%
#  addTiles() %>%  # Add default OpenStreetMap map tiles
#  addMarkers(lng=Tickets$lon, lat=Tickets$lat, popup=(Tickets_N))
#t 
Tickets_N <- paste(Tickets$Tickets_Names,"--",Tickets$Match_Time,"--","€",Tickets$Tickets_Price)

df.20 <- Tickets[1:nrow(Tickets),]

getColor <- function(Tickets) {
  sapply(Tickets$League, function(League) {
    if(League == "uefa-europa-league") {
      "green"
    } else if(League =="la-liga") {
      "purple"
    }else if(League =="serie-a") {
      "white"
    } else if(League =="premier-league") {
      "pink"
    }else if(League =="bundesliga") {
      "red"
    }else if(League =="french-ligue-1") {
      "darkblue"
    }else if(League =="2018-world-cup") {
      "orange"
    }else if(League =="2017-confederations-cup") {
      "lightblue"
    }else {
      "black"
    } })
}

icons <- awesomeIcons(
  icon = 'ios-football',
  iconColor = 'black',
  library = 'ion',
  markerColor = getColor(df.20)
)

colour <- c("lightblue","orange","red","darkblue","purple","pink","white","green")
pal <- colorFactor(colour,League)

leaflet(df.20) %>% addTiles() %>%
  addAwesomeMarkers(~lon, ~lat, icon=icons, label=~as.character(Tickets_N))%>%
  addLegend("bottomright", pal = pal, values = ~League,
            title = "Leagues",
            labFormat = labelFormat(prefix = ""),
            opacity = 1
  )
```

   
Football Matches according to Teams
=====================================  


```{r}
#"barcelona-fc","real-madrid","atletico-de-madrid","juventus-fc","as-roma","ac-milan","arsenal-fc",
#"chelsea-fc","liverpool-fc","manchester-united","bayern-munich","paris-saint-germain"

Ticketteam <- function(Team_Name){
  url <- paste("http://www.sportsevents365.com/dock/team/", 
               Team_Name, sep="")
  webpage <- read_html(url)
  Team <- data.frame()
  Tickets_Names = webpage%>% html_nodes(css=".colorA span") %>% html_text()
  Tickets_Names <- gsub("\n","",Tickets_Names)
  Tickets_Names <- gsub("\t","",Tickets_Names)
  Tickets_Names <- gsub(" ","",Tickets_Names)
  Tickets_Names = as.data.frame(Tickets_Names)
  Location = webpage%>% html_nodes(css=".eventLocation div") %>% html_text()
  Location <- gsub("\n","",Location)
  Location <- gsub("\t","",Location)
  Location <- gsub(" ","",Location)
  Location_Coordinates <- geocode(Location)
  Location = as.data.frame(Location)
  Match_Time = webpage%>% html_nodes(css=".icon+ span") %>% html_text()
  Match_Time <- gsub(",","",Match_Time)
  #Match_Time <- as.Date(Match_Time, format = "%d %b %Y")
  Match_Time = as.data.frame(Match_Time)
  Tickets_Price = webpage%>% html_nodes(css=".stories .tableCell:nth-child(3)") %>% html_text()
  Tickets_Price <- gsub("from","",Tickets_Price)
  Tickets_Price <- gsub("€","",Tickets_Price)
  Tickets_Price <- gsub("\n","",Tickets_Price)
  Tickets_Price <- gsub("\t","",Tickets_Price)
  Tickets_Price <- as.numeric(Tickets_Price)
  Tickets_Price <- as.data.frame(Tickets_Price)
  All = cbind(Tickets_Names ,Location ,Location_Coordinates,
              Match_Time ,Tickets_Price )
  All = as.data.frame(All)
  Team <- rbind(Team, All)
  Team_N <- paste(Team$Tickets_Names,"--",Team$Match_Time,"--","€",Team$Tickets_Price)
  m <- leaflet() %>%
    addTiles() %>%  # Add default OpenStreetMap map tiles
    addMarkers(lng=Team$lon, lat=Team$lat, popup=(Team_N))
  m
}
```


```{r}
Text_Team <- function(Team_Name){
  url <- paste("http://www.sportsevents365.com/dock/team/", 
               Team_Name, sep="")
  webpage <- read_html(url)
  Text = webpage%>% html_nodes(css="p:nth-child(1)") %>% html_text()
  print(Text[1])
  }
```



### Barcelona Fc

```{r}
Text_Team("barcelona-fc")
```

    
```{r}
Ticketteam("barcelona-fc")
```
    
### Real Madrid

```{r}
Text_Team("real-madrid")
```


```{r}
Ticketteam("real-madrid")
```

### Atletico de Madrid

```{r}
Text_Team("atletico-de-madrid")
```


```{r}
Ticketteam("atletico-de-madrid")
```

### Juventus FC

```{r}
Text_Team("juventus-fc")
```


```{r}
Ticketteam("juventus-fc")
```

### As Roma

```{r}
Text_Team("as-roma")
```


```{r}
Ticketteam("as-roma")
```

### Ac Milan

```{r}
Text_Team("ac-milan")
```


```{r}
Ticketteam("ac-milan")
```

### Arsenal FC

```{r}
Text_Team("arsenal-fc")
```


```{r}
Ticketteam("arsenal-fc")
```

### Chelsea FC

```{r}
Text_Team("chelsea-fc")
```


```{r}
Ticketteam("chelsea-fc")
```

### Liverpool FC

```{r}
Text_Team("liverpool-fc")
```


```{r}
Ticketteam("liverpool-fc")
```

### Manchester United

```{r}
Text_Team("manchester-united")
```


```{r}
Ticketteam("manchester-united")
```

### Bayern Munich

```{r}
Text_Team("bayern-munich")
```


```{r}
Ticketteam("bayern-munich")
```

### Paris Saint Germain

```{r}
Text_Team("paris-saint-germain")
```


```{r}
Ticketteam("paris-saint-germain")
```

Football Matches according to Competition
=====================================     

```{r}
Ticketleague <- function(League_Name){
  url <- paste("http://www.sportsevents365.com/dock/competition/", 
               League_Name, sep="")
  webpage <- read_html(url)
  Ticketss <- data.frame()
  Tickets_Names = webpage%>% html_nodes(css=".colorA span") %>% html_text()
  Tickets_Names <- gsub("\n","",Tickets_Names)
  Tickets_Names <- gsub("\t","",Tickets_Names)
  Tickets_Names <- gsub(" ","",Tickets_Names)
  Tickets_Names = as.data.frame(Tickets_Names)
  Location = webpage%>% html_nodes(css=".eventLocation div") %>% html_text()
  Location <- gsub("\n","",Location)
  Location <- gsub("\t","",Location)
  Location <- gsub(" ","",Location)
  Location_Coordinates <- geocode(Location)
  Location = as.data.frame(Location)
  Match_Time = webpage%>% html_nodes(css=".icon+ span") %>% html_text()
  Match_Time <- gsub(",","",Match_Time)
  #Match_Time <- as.Date(Match_Time, format = "%d %b %Y")
  Match_Time = as.data.frame(Match_Time)
  Tickets_Price = webpage%>% html_nodes(css=".stories .tableCell:nth-child(3)") %>% html_text()
  Tickets_Price <- gsub("from","",Tickets_Price)
  Tickets_Price <- gsub("€","",Tickets_Price)
  Tickets_Price <- gsub("\n","",Tickets_Price)
  Tickets_Price <- gsub("\t","",Tickets_Price)
  Tickets_Price <- as.numeric(Tickets_Price)
  Tickets_Price <- as.data.frame(Tickets_Price)
  All = cbind(Tickets_Names ,Location ,Location_Coordinates,
              Match_Time ,Tickets_Price )
  All = as.data.frame(All)
  Ticketss <- rbind(Ticketss, All)
  Ticketss_N <- paste(Ticketss$Tickets_Names,"--",Ticketss$Match_Time,"--","€",Ticketss$Tickets_Price)
  n <- leaflet() %>%addTiles() %>%addMarkers(lng=Ticketss$lon, lat=Ticketss$lat, popup=(Ticketss_N),popupOptions(color="black"))
  return(n)
}
```

```{r}
Text_League <- function(League_Name){
  url <- paste("http://www.sportsevents365.com/dock/competition/", 
               League_Name, sep="")
  webpage <- read_html(url)
  Text = webpage%>% html_nodes(css="p:nth-child(1)") %>% html_text()
  print(Text[1])
  }
```


### La Liga

```{r}
Text_League("la-liga")
```

    
```{r}
Ticketleague("la-liga")
```
    
### Uefa Europa League

```{r}
Text_League("uefa-europa-league")
```


```{r}
Ticketleague("uefa-europa-league")
```

### Serie A

```{r}
Text_League("serie-a")
```


```{r}
Ticketleague("serie-a")
```

### Premier League

```{r}
Text_League("premier-league")
```


```{r}
Ticketleague("premier-league")
```

### Bundesliga

```{r}
Text_League("bundesliga")
```


```{r}
Ticketleague("bundesliga")
```

### French Ligue 1 

```{r}
Text_League("french-ligue-1")
```


```{r}
Ticketleague("french-ligue-1")
```

### 2018 World Cup

```{r}
Text_League("2018-world-cup")
```


```{r}
Ticketleague("2018-world-cup")
```

### 2017 Confederations Cup

```{r}
Text_League("2017-confederations-cup")
```


```{r}
Ticketleague("2017-confederations-cup")
```


Top 25 Most Expensive Players
===================================== 

```{r}
url <- paste("https://www.transfermarkt.co.uk/spieler-statistik/wertvollstespieler/marktwertetop?land_id=0&ausrichtung=alle&spielerposition_id=alle&altersklasse=alle&plus=1")
webpage <- read_html(url)
Player_Names = webpage%>% html_nodes(css=".spielprofil_tooltip") %>% html_text()
Player_Names = as.data.frame(Player_Names)
Games_Played = webpage%>% html_nodes(css=".hauptlink+ .zentriert") %>% html_text()
Games_Played = as.data.frame(Games_Played)
Position = webpage%>% html_nodes(css=".inline-table tr+ tr td") %>% html_text()
Position = as.data.frame(Position)
Age = webpage%>% html_nodes(css=".zentriert:nth-child(3)") %>% html_text()
Age <- Age[-1]
Age <- as.numeric(Age)
Age <- as.data.frame(Age)
Market_Value = webpage%>% html_nodes(css="#yw1 b") %>% html_text()
Market_Value <- gsub("£","",Market_Value)
#Market_Value <- gsub(".","",Market_Value)
Market_Value <- gsub("m","",Market_Value)
Market_Value <- as.numeric(Market_Value)
Market_Value <- as.data.frame(Market_Value)
Goals = webpage%>% html_nodes(css=".zentriert:nth-child(8)") %>% html_text()
Goals <- Goals[-1]
Goals <- as.numeric(Goals)
Goals <- as.data.frame(Goals)
Assists = webpage%>% html_nodes(css=".zentriert:nth-child(10)") %>% html_text()
Assists <- Assists[-1]
Assists <- as.numeric(Assists)
Assists <- as.data.frame(Assists)
  
Player_Table = cbind(Player_Names ,Position,Age,Market_Value,Games_Played,
               Goals,Assists)

```
### Data

```{r}
qplot(1:15, 1:15, geom = "blank") + theme(line = element_blank(), text = element_blank()) +annotation_custom(grob = tableGrob(Player_Table[1:15,],theme = ttheme_default(base_size = 6)))
```

### Player Names vs Goals (Top 10)
 
```{r}
ggplot(Player_Table[1:10,],aes(Player_Names,Goals)) +
  geom_density()+ coord_flip()
```

### Goals vs Game Played

```{r}
ggplot(Player_Table, aes(x =Goals,color=Player_Names))+ geom_point(aes(y=Games_Played),size=2)
```

### Market value vs Age

```{r}
PA <- ggplot(Player_Table, aes(x = Age, y =Market_Value ),size=2)
PA + geom_point(aes(color = Player_Names))+theme(text = element_text())+geom_smooth(col= "black")

```

### Asists vs Goals Plot of The Players on The Left Wing

```{r}
ggplot(subset(Player_Table,
              Position=="Left Wing"),aes(x=Goals,y=Assists,color=Player_Names))+geom_point()
```

### Boxplot Goals vs Assists

```{r}
boxplot(Player_Table$Goals,Player_Table$Assists, xlab="Goals                                                      Assists")
```

